---
title: "R Notebook"
output: html_notebook
---
```{r}
library(dplyr)
library(ggplot2)
library(data.table)
```

```{r}
df <- df2[, c("Q2.2", "Q164")]
head(df)
str(df) #check variable type
```

```{r}
### to remove NAs first convert factors!
df <- df %>% mutate_if(is.factor, as.character)
df <- df[!is.na(df$Q164) , ]
df <- df[df$Q164 != "NA" , ]

#check NA is not present
unique(df$Q2.2)
unique(df$Q164)

### convert back to factor for analysis
df$Q164 <- factor(df$Q164, levels = c("0", "1-2", "3-5", "6-10", "11-20", "More than 20", ordered = TRUE))
df$Q2.2 <- factor(df$Q2.2, levels= c("Android", "iOS (iPhone)"))
summary(df)
```

### Perform Test for statistical significance between the groups

#### Kruskal Wallis
One independent variable with two or more levels. The test is more commonly used when there are three or more levels. For two levels instead of the Kruskal-Wallis test consider using the Mann Whitney U Test.
```{r}
# result = kruskal.test(Q164 ~ Q2.2,   data = df) 
# print(result)
# do not apply this test as there are only 2 groups
```

```{r}
# 
# install.packages("dplyr" ,dependencies = TRUE) 
# install.packages(c("Rcpp","tidyverse"))
# library(tidyverse)
install.packages("ggpubr") 
# library(ggpubr)
# library(rstatix)
# df %>% group_by(Q164) %>% get_summary_stats(Q2.2, type = "common")
```
#### Mann Whitney U Test
- It is a popular nonparametric (distribution-free) test to compare outcomes between two independent groups.
- When comparing two independent samples, when the outcome is not normally distributed and the samples are small, a nonparametric test is appropriate. 
- It is used to see the distribution difference between two independent variables on the basis of an ordinal(categorical variable having intrinsic an order or rank) dependent variable. 
- The major difference between the Mann-Whitney U and the Kruskal-Wallis H is simply that the latter can accommodate more than two groups. Both tests require independent (between-subjects) designs and use summed rank scores to determine the results.


```{r}
df$Q164 <- as.numeric(df$Q164)
unique(df$Q164)
res <- wilcox.test(Q164 ~Q2.2,  data = df, paired= FALSE )

w <-  166 * 38 /2
print(res)
print(w)
```

p-value : significance value used to determine if null hypothesis should be rejected (i.e. p <0.05 -> reject  Null hypothesis)
the medians are not all that far from one another: look at the value of the U-statistic we can see it is reasonably close to w (n1*n2/2).
Failed to reject null hypothesis -> ditributions are identical
[Source](https://miningthedetails.com/blog/r/non-parametric-tests/)


### Extras
```{r}
summary(df$Q2.2)
# unique(df$Q164)
```
```{r}
table(df$Q164, df$Q2.2)
100*prop.table(table(df$Q164, df$Q2.2))

count <- df %>% count(Q164, Q2.2)
for(i in 1:nrow(count)){
  if(i%%2==0){
      count[i,c("per")] <- 100*(count[i,c("n")] / 38)
  }
  else{
     count[i,c("per")] <- 100*(count[i,c("n")] / 166)
  }
}
count$per <- round(count$per, 2)
setnames(count, old = c("Q2.2"), new = c('key'))

image <- ggplot(count, aes(Q164, y = per , fill= key)) +geom_bar(stat='identity', position='dodge') +  labs(x = "Negative Experience",  y = "Percentage of Participants") + theme(axis.text.x = element_text(face = "bold", color = "#993333", size = 9, angle = 15)) + geom_text(aes(label = per), position = position_dodge(0.9),vjust = 1.5)
plot(image)
```
#### Relation to different smartphone features use
```{r}
df <- copy[, c("Q2.2","Q3.2_1","Q3.2_2" , "Q3.2_3" , "Q3.2_4" ,"Q3.2_5")]
df$Q2.2 <- factor(df$Q2.2, levels= c("Android", "iOS (iPhone)"))
# summary(df)
df <- df[! is.na(df$Q3.2_1 ), ]
df <- df[! is.na(df$Q3.2_2 ), ]
df <- df[! is.na(df$Q3.2_3 ), ]
df <- df[! is.na(df$Q3.2_4 ), ]
df <- df[! is.na(df$Q3.2_5 ), ]


count <- df %>%  group_by(df$Q2.2) %>% summarise_all(funs(mean))
count <- count[, -2]
count<- round(count[, 2:6],2)

result2 = kruskal.test(Q3.2_1 ~ Q2.2,   data = df) 
print(result2)

result2 = kruskal.test(Q3.2_2 ~ Q2.2,   data = df) 
print(result2)

result2 <- kruskal.test(Q3.2_3 ~ Q2.2,   data = df) 
print(result2)

result2 <- kruskal.test(Q3.2_4 ~ Q2.2,   data = df) 
print(result2)

result2 <- kruskal.test(Q3.2_5 ~ Q2.2,   data = df) 
print(result2)

# av <- aov(Q2.2~ Q3.2_1+Q3.2_2 + Q3.2_3+ Q3.2_4+ Q3.2_5  , data = df) 
# summary(av)
```




