---
title: "Last Notification"
output: html_notebook
---

```{r}
require(dplyr)
library(ggplot2)
library(stringr)
```

```{r}
df <- df2[  , c("Q4.2")]
df$Negative_experiences <- df2$Q164 
head(df)
```

#### Types of Apps the last notification came from
```{r}
unique(df$Q4.2)
```


### Concern if someone else see the notification!!
```{r}
dfx <- df2[, c("Q175")]
class(dfx$Q175)
dfx$Q175 <- (as.character(dfx$Q175))
dfx$Q175[ is.na(dfx$Q175) ] <- "Not reported"
unique(dfx$Q175)

dfx[] <- lapply(dfx, factor,  levels = c("Extremely concerned", "Somewhat concerned", "Neither concerned nor unconcerned", "Somewhat unconcerned", "Completely unconcerned", "Not reported")) 

c <-as.data.frame(100*prop.table(table(dfx)))
c$Freq <- round(c$Freq)

# remove Not reported
c <- c[1:5, ]
```

#### Plot for: Participants' level of concern if someone else viewed the latest notification they received.
```{r}
img <- ggplot(c, aes(x = dfx, y= Freq )) + geom_bar(width=0.5, stat="identity", fill = "cornflowerblue",color="black")+ 
  labs( x= "Likert Scale",  y = "Percentage of Participants") + 
  theme(axis.text.x = element_text(color = "black", size = 16, angle = 0), axis.title.y = element_text(size = 17, angle = 90),  axis.title.x= element_blank(), axis.text.y = element_text(color = "black", size = 16, angle = 0), panel.background = element_rect(fill ="white"), panel.grid.major = element_blank(), panel.grid.minor = element_blank() ,axis.line = element_line()) + geom_text(aes(label = paste0(Freq, "%") ),vjust = -0.5, size= 8) + scale_x_discrete(labels = function(dfx) str_wrap(dfx, width = 5)) + coord_cartesian(ylim = c(0, 50)) + scale_y_continuous(breaks = seq(0,50, 10))
plot(img)

```

```{r}
pdf(file="Last2_version2.pdf", width = 8) #save to pdf
plot(img)
dev.off()
```

### Does notification contain information of someone else
```{r}
dfx <- df2[, c("Q4.3","Q4.4")]
head(dfx)
unique(dfx$Q4.4)
```

```{r}
df <- dfx[dfx$Q4.3 == "Yes",2 ]
head(df)
df$Q4.4 <- as.character(df$Q4.4)
df$Q4.4[ is.na(df$Q4.4) ] <- "Not reported"
unique(df$Q4.4)
```
Extremely concerned               Not at all concerned             
[4] Somewhat unconcerned              Neither concerned nor unconcerned Somewhat concerned 

```{r}
df[] <- lapply(df, factor,  levels = c("Extremely concerned", "Somewhat concerned", "Neither concerned nor unconcerned", "Somewhat unconcerned", "Not at all concerned", "Not reported")) 

c <-as.data.frame(100*(prop.table(table(df))))
c$Freq <- round(c$Freq)

c<- c[1:5, ] #remove not reported from plot
c$df  <- as.character(c$df)
c[5,1] = "Completely unconcerned"
c$df <- factor(c$df, levels = c("Extremely concerned", "Somewhat concerned", "Neither concerned nor unconcerned", "Somewhat unconcerned","Completely unconcerned"), ordered = TRUE)

```


```{r}
img <- ggplot(c, aes(x = df, y= Freq )) + geom_bar(width=0.5, stat="identity", fill = "cornflowerblue",color="black")+ 
  labs( x = "Likert Scale", y = "Percentage of Participants") + 
  theme(axis.text.x = element_text(color = "black", size = 16, angle = 0), axis.title.y = element_text(size = 17, angle = 90), axis.text=element_text(color = "black",size=16),axis.title.x=element_blank(), panel.background = element_rect(fill ="white"), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.line = element_line()) + geom_text(aes(label =  paste0(Freq, "%") ),vjust = -0.5, size=9)+ scale_x_discrete(labels = function(df2) str_wrap(df2, width = 5)) + coord_cartesian(ylim = c(0, 50))
plot(img)
# img <- ggplot(c, aes(x = dfx, y= Freq )) + geom_bar(width=0.5, stat="identity", fill = "cornflowerblue",color="black")+ 
#   labs( x= "Likert Scale",  y = "Percentage of Participants") + 
#   theme(axis.text.x = element_text(color = "black", size = 17.5, angle = 0), axis.title.y = element_text(size = 17, angle = 90),  axis.title.x= element_blank(), axis.text.y = element_text(color = "black", size = 16, angle = 0), panel.background = element_rect(fill ="white"), panel.grid.major = element_blank(), panel.grid.minor = element_blank() ,axis.line = element_line()) + geom_text(aes(label = paste0(Freq, "%") ),vjust = -0.5, size= 8) + scale_x_discrete(labels = function(dfx) str_wrap(dfx, width = 5)) + coord_cartesian(ylim = c(0, 100))
# plot(img)

# png("Last3.png", 1080, 900)
# plot(img)
# dev.off()
```

```{r}
pdf(file="Last3_version3.pdf", width = 8)
plot(img)
dev.off()
```

#### the number of participants in each group
```{r}
c <-as.data.frame(((table(df))))
```

### Extras: not used in analysis
##### How users interacted with last notification
```{r}
# How quickly did you address the notification after you first saw it?
print(df[df$Q4.7 == "Other: (Please specify:)", ]) 
# 2 mentioned haven't addressed it yet
```

```{r}
df <- df[!is.na(df$Q4.7) , ]
unique(df$Q4.7)
df$Q4.7 <- as.character(df$Q4.7)
df$Q4.7[! is.na(df$Q4.7_0_TEXT) ] <- "Didn't address it"

dfx <- as.data.frame(df$Q4.7)
dfx <- drop_na(dfx)
colnames(dfx) <- "s"
dfx[] <- lapply(dfx, factor,  levels = c("within a minute", "within 5 minutes", "within 30 minutes", "within an hour", "within 6 hours", "within 12 hours", "within 24 hours", "Didn't address it")) 

image3 <- ggplot(dfx, aes(x = s)) +   geom_bar(aes(y = 100*(..count..)/sum(..count..)), fill = "#993333",color="black") +  labs(x = "Frequency",  y = "% Participants") + theme(axis.text.x = element_text( color = "#993333", size = 20, angle = 15), axis.title.y = element_text(size = 20, angle = 90), axis.text=element_text(size=20),axis.title=element_text(size=20,face="bold"))

100* prop.table(table(dfx))

plot(image3)
png("image3.png", 1080, 900)
print(image3)
dev.off()

rm(dfx)
```




