---
title: "Partcipants"
---
### Preprocessing of data, Demographics 
### 'df2', 'copy' are the filtered dataframe used in other scripts
```{r}
library(qualtRics)
library(httr)
Sys.getenv("QUALTRICS_BASE_URL")
url <- qualtRics:::create_surveys_url("iu.co1.qualtrics.com")
qualtrics_api_credentials(api_key = " ", base_url = "iu.co1.qualtrics.com",overwrite  = TRUE, install = TRUE)
```

```{r}
readRenviron("~/.Renviron")
```

```{r}
library(ggplot2)
library(tidyselect)
library("dplyr") #includes functions for selecting, filtering, grouping, and arranging data like mutate
library("magrittr") # required for caoalesce function
library(dplyr)
library(ggplot2)
library(data.table)
library(tidyr)
library(reshape2)
```

```{r}
mysurvey <- fetch_survey(surveyID = all_surveys()$id[2], verbose = TRUE)
df2 <- mysurvey
```

#### check duplicate IP Addresses
```{r}
sprintf("no. of unique responses: %d and total filtered responses: %d", length(unique(df2$IPAddress)) ,nrow(df2) )
```
#### remove duplicate IP Addresses
```{r}
df2 <- df2[!duplicated(df2$IPAddress), ] 
#keeps the first row of all rows among duplicate rows
```

#### Check for Country code = US
```{r}
freegeoip <- function(ip, format = ifelse(length(ip)==1,'list','dataframe'))
{
  if (1 == length(ip))
  {
    # a single IP address
    require(rjson)
    url <- paste(c("http://freegeoip.live/json/", ip), collapse='')
    ret <- fromJSON(readLines(url, warn=FALSE))
    if (format == 'dataframe')
      ret <- data.frame(t(unlist(ret)))
    return(ret)
  } 
  else {
    ret <- data.frame()
    for (i in 1:length(ip))
    {
      r <- freegeoip(ip[i], format="dataframe")
      ret <- rbind(ret, r)
    }
    return(ret)
  }
}

ipaddresses <- as.vector(df2$IPAddress)
ips <- as.data.frame(freegeoip(ipaddresses))
```

```{r}
#create a list of IP Addresses outside of US
to_remove <- as.vector(ips[ips$country_code != "US", c("ip") ])
print(to_remove)

#remove the two IP address not from US
df2 <- df2[df2$IPAddress!= "122.173.50.157",]
df2 <- df2[df2$IPAddress!= "45.143.144.99",]
df2 <- df2[df2$IPAddress!= "52.95.75.4",]
df2 <- df2[df2$IPAddress!= "134.202.34.132",]
```

#### Filtering out data
```{r}
#filtered for committment ques, Phone OS and attention checks
df2 <- df2[df2$Q1.2 == "I will provide my best answers." & df2$Q3.8 == "Translate" & df2$Q5.1_5 == "Somewhat agree" , ]
df2 <- df2[df2$Q2.2 != "Other: (Please specify:)",] #smartphone operating system is not iOS or Android
df2 <- df2[!is.na(df2$Q1.2), ]
df2 <- df2[!is.na(df2$Q3.8), ]
df2 <- df2[!is.na(df2$Q3.8), ]
```

###Filtered tables
```{r}
copy <- df2 
#copy and df2 are the filtered data used for analysis everywhere
```

#### Completion time in seconds
```{r}
dft <- copy
a <- mean(dft$`Duration (in seconds)`)
b<- median(dft$`Duration (in seconds)`)
sprintf("Mean survey completion time: %f min %f sec, Median completion time: %f min %f sec", a/60, a %% 60, b/60, b%%60  )
```

### Demographics

####Age
```{r}
age <- as.data.frame(2020 - copy$Q11.2) #calculate age from the year of birth
sprintf("Age characteristics: Range: %f to %f , Mean: %f, Median: %f",min(age$`2020 - copy$Q11.2`, na.rm = TRUE), max(age$`2020 - copy$Q11.2`, na.rm = TRUE), mean(age$`2020 - copy$Q11.2`, na.rm = TRUE), median(age$`2020 - copy$Q11.2`, na.rm = TRUE))
rm(age)
```

####Gender
```{r}
table(df2$Q11.3,useNA = c("always")) #frequencies
100*prop.table(table(df2$Q11.3, useNA = c("always"))) #proportion
```

####Ethnicity

```{r}
# head(copy)
# colnames(mysurvey)
ethnicity<- df2 %>% mutate(Q11.4_0 = coalesce( Q11.4_0_TEXT, Q11.4_0), .keep= "unused")
```

```{r}
ethnicity <- ethnicity %>% mutate(Q11.4 = coalesce(Q11.4_1, Q11.4_2, Q11.4_3, Q11.4_4, Q11.4_5, Q11.4_6, Q11.4_0, Q11.4_8), .keep="unused")
```

```{r}
print(ethnicity$Q11.4) #check the colesced columns
```

```{r}
table(ethnicity$Q11.4, useNA = c("always"))
100*prop.table(table(ethnicity$Q11.4, useNA = c("always")))
```

#### Profession
```{r}
table(copy$Q11.8, useNA = c("always")) #frequencies
unique(copy$Q11.8)
```

#### Marital Status
```{r}
table(copy$Q11.13,useNA = c("always")) #frequencies
100*prop.table(table(copy$Q11.13, useNA = c("always"))) #proportio
```

#### people in household
```{r}
table(copy$Q11.12, useNA = c("always")) #frequencies
100*prop.table(table(copy$Q11.12, useNA = c("always"))) #proportio
```

#### years in US
```{r}
table(copy$Q11.11, useNA = c("always")) #frequencies
100*prop.table(table(copy$Q11.11)) #proportio
```

#### level of education
```{r}
table(copy$Q11.5, useNA = c("always"))
100*prop.table(table(copy$Q11.5, useNA = c("always")))

table(copy$Q11.5) #frequencies
100*prop.table(table(copy$Q11.5)) #proportio
```

#### level of education
```{r}
unique(copy$Q11.9) #frequencies
100*prop.table(table(copy$Q11.9)) #proportio

df <- copy[, c("Q11.9")]
```


#### Extras


##### Income
```{r}
table(copy$Q11.10) #frequencies
#prop.table(table(copy$Q11.10)) #proportio
sprintf( "N= %d , percantage= %f", table(copy$Q11.10),100* prop.table(table(copy$Q11.10))  )
```

```{r}
image2 <- ggplot(copy, aes(x = Q11.10)) + geom_bar(fill = "cornflowerblue",color="black") + labs(x = "Income brackets",  y = "Participants count", title = "Income Distribution") + theme(axis.text.x = element_text(face = "bold", color = "#993333", size = 12, angle = 90))
plot(image2)
png("image2.png")
print(image2)
dev.off()
```


##### remove unused variables from env
```{r}
rm(list = ls(pattern = "^ipa"))
rm(ethnicity)
rm(gender)
rm(ips)
rm(to_remove)
```

[Commands Source](https://uc-r.github.io/descriptives_categorical#frequencies)
