---
title: "MUIPC score"
output: html_notebook
---
```{r}
# if(!require(psych)){install.packages("psych")}
# if(!require(likert)){install.packages("likert")}
library(ggplot2)
require(dplyr)
```

### Calculating  the MUIPC score

```{r}
df_m <- copy[  , c("Q5.1_1","Q5.1_2" ,"Q5.1_3" ,"Q5.1_4" ,"Q5.1_6" ,"Q5.1_7", "Q164")]
# "Q5.1_5" was an attention check question
# Q164 was the number of negative experiences due to notifications

```

```{r}
#filter out NA values
df_m[, 1:6][is.na(df_m[, 1:6])] <- "N/A"

df_m <- df_m[ df_m$Q5.1_1!= "N/A" , ]
df_m <- df_m[ df_m$Q5.1_2!= "N/A" , ]
df_m <- df_m[ df_m$Q5.1_3!= "N/A" , ]
df_m <- df_m[ df_m$Q5.1_4!= "N/A" , ]
df_m <- df_m[ df_m$Q5.1_6!= "N/A" , ]
df_m <- df_m[ df_m$Q5.1_7!= "N/A" , ]

df_m$Q164 <- as.character(df_m$Q164)
df_m <- df_m[(df_m$Q164 )!= "N/A", ]
df_m <- df_m[! is.na(df_m$Q164 ), ]
unique(df_m$Q164)

#Factor the columns
df_m$Q5.1_1 <- factor(df_m$Q5.1_1, levels = c("Strongly disagree", "Disagree", "Somewhat disagree", "Neither agree nor disagree", "Somewhat agree", "Agree", "Strongly agree"), ordered = TRUE)
df_m$Q5.1_2 <- factor(df_m$Q5.1_2, levels = c("Strongly disagree","Disagree", "Somewhat disagree","Neither agree nor disagree", "Somewhat agree", "Agree", "Strongly agree"), ordered = TRUE)
df_m$Q5.1_3 <- factor(df_m$Q5.1_3, levels = c("Strongly disagree","Disagree", "Somewhat disagree","Neither agree nor disagree",  "Somewhat agree", "Agree", "Strongly agree"), ordered = TRUE)
df_m$Q5.1_4 <- factor(df_m$Q5.1_4, levels = c("Strongly disagree", "Disagree","Somewhat disagree", "Neither agree nor disagree","Somewhat agree",  "Agree",  "Strongly agree"), ordered = TRUE)
df_m$Q5.1_6 <- factor(df_m$Q5.1_6, levels = c("Strongly disagree", "Disagree","Somewhat disagree", "Neither agree nor disagree",  "Somewhat agree","Agree", "Strongly agree"), ordered = TRUE)
df_m$Q5.1_7 <- factor(df_m$Q5.1_7, levels = c("Strongly disagree","Disagree", "Somewhat disagree", "Neither agree nor disagree",  "Somewhat agree", "Agree", "Strongly agree"), ordered = TRUE)
df_m$Q164 <- factor(df_m$Q164, levels = c("0", "1-2", "3-5", "6-10", "11-20", "More than 20", ordered= TRUE  ))
```

```{r}
summary(df_m)
str(df_m)
```

```{r}
df_m <- df_m %>% mutate_if(is.factor, as.numeric)
str(df_m)
```


```{r}
#Find the score values for each users
df_m <- df_m %>% mutate(survelScore = rowSums(.[1:3]) )
df_m <- df_m %>% mutate(intrusionScore = rowSums(.[4:6]) )

#group the score by the number of negative experiences 
mean_df_surv <- df_m %>%  group_by(df_m$Q164) %>% summarise(mean_SurvelScore = round( mean(survelScore, na.rm = TRUE), 2))
mean_df_intr <- df_m %>%  group_by(df_m$Q164) %>% summarise(mean_intrusionScore = round( mean(intrusionScore, na.rm = TRUE),2))
# df_m %>%  group_by(df_m$Q164) %>% summarise(mean_intrusionScore = mean(intrusionScore, na.rm = TRUE), median_intrusionScore = median(intrusionScore, na.rm = TRUE))
```

#### correlation
```{r}
t <- cor.test(df_m$Q164, df_m$intrusionScore, method = "spearman",exact=FALSE)
t

t <- cor.test(df_m$Q164, df_m$survelScore, method = "spearman",exact=FALSE)
t

# https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/cor.test
```


#### Check for Normality of data 
```{r}
# df_m %>%  group_by(df_m$Q164) %>% summarise(table(df_m$Q164, df_m$survelScore) )
# (table(df_m$survelScore))

# table(df_m$Q164, df_m$survelScore)
table( df_m$survelScore)
table(df_m$Q164) #Not normal distribution


shapiro.test(df_m$Q164)
shapiro.test(df_m$intrusionScore)
shapiro.test(df_m$survelScore) 
# => less than 0.05. reject null hypothesis. deviates significantly from normal distribution
``` 



### Extras 


#### AOV analysis
```{r}
one.way <- aov(Q164 ~ Q5.1_1+Q5.1_2 + Q5.1_3+ Q5.1_4+ Q5.1_6 + Q5.1_7 , data = df_m)
summary(one.way)

a1 <- aov(Q164 ~ survelScore, data = df_m)
summary(a1)

b1 <- aov(Q164 ~ intrusionScore, data = df_m)
summary(b1)

c1 <- aov(Q164 ~ survelScore + intrusionScore, data= df_m)
summary(c1)


```


- The Kruskal-Wallis H test (sometimes also called the "one-way ANOVA on ranks") is a rank-based nonparametric test that can be used to determine if there are statistically significant differences between two or more groups of an independent variable on a continuous or ordinal dependent variable.
```{r}


result = kruskal.test(Q164 ~ survelScore   ,   data = df_m) 
print(result)


result = kruskal.test(Q164 ~ intrusionScore  ,   data = df_m) 
print(result)
```






```{r}

# cmatrix = cor(df_m, method = c("spearman"))
# cpearson_matrix = cor(df_m, method = c("pearson"))
# round(cmatrix,2)
# round(cpearson_matrix, 2)
```

```{r}
# source("http://www.sthda.com/upload/rquery_cormat.r")
# rquery.cormat(df_m)
# 
# 
# 
# library(reshape2)
# library(data.table)
# # setnames(df_m, old = c("Q5.1_1","Q5.1_2", "Q5.1_3", "Q5.1_4", "Q5.1_6", "Q5.1_7", "Q164"), new = c('Q1','Q2', 'Q3', 'Q4', "Q5", "Q6", "Neg_Exp"))
# 
# install.packages("corrplot")
# library(corrplot)
# corrplot(cmatrix)
# corrplot(cpearson_matrix)
```



### Compare no of negative experience with MUIPC Score
```{r}
df_m$Negative_experiences <- copy$Q164
df_m <- df_m[!is.na(df_m$survelScore), ] # remove rows having NA values marked
df_m <- df_m[!is.na(df_m$intrusionScore), ] # remove rows having NA values marked

df_m <- df_m[!is.na(df_m$Negative_experiences), ]
unique(df_m$Negative_experiences)
```


```{r}
mean(df_m$survelScore)
median(df_m$survelScore)
mean(df_m$intrusionScore)
median(df_m$intrusionScore)
```

#### Find out correlation
```{r}
df_m$Negative_experiences <- as.character(df_m$Negative_experiences)
is.character(df_m$Negative_experiences)
unique(df_m$Negative_experiences)

df_m <- df_m[df_m$Negative_experiences != "NA", ]
df_m <- df_m[!is.na(df_m$Negative_experiences), ]
```

```{r}
rm(df_m)
```








