 ---
title: "R Notebook"
output: html_notebook
---
### Smartphone Features Usage Analysis
```{r}
df2_ <- copy
df2_ <- df2_[  , c("Q3.2_1","Q3.2_2" , "Q3.2_3" , "Q3.2_4" ,"Q3.2_5")]
```

### usage analysis of different features 
```{r}
# DND Mode
tab_count <- table(df2_$Q3.2_1, useNA = c("always"))
tab_per <- 100*prop.table(table((df2_$Q3.2_1), useNA = c("always")))
print(tab_per)
print(tab_per[["0"]])
print(tab_per[17]) #percentage of users who don't use DND mode i.e. use of 0 hours in a typical day
sprintf("atleast once %f percent N = %d", 100 - tab_per[["0"]] -tab_per[17] , nrow(df2_)- tab_count[["0"]]-tab_count[17] )
#total - those who use for 0 hours - those who did not report
```

```{r}
# Silent Mode
tab_count <- table(df2_$Q3.2_2,useNA = c("always"))
tab_per <-  100*prop.table(table((df2_$Q3.2_2),useNA = c("always")))
print(tab_per)
print(tab_per[["0"]])
print(tab_per[23])
sprintf("atleast once %f percent N = %d", 100 - tab_per[["0"]]-tab_per[23], nrow(df2_)-tab_count[["0"]]-tab_count[23] )
#total - those who use for 0 hours - those who did not report
```

```{r}
# Turn off
tab_count <- table(df2_$Q3.2_3,useNA = c("always"))
tab_per <-  100*prop.table(table((df2_$Q3.2_3),useNA = c("always")))
print(tab_per)
print(tab_per[["0"]])
print(tab_per[18])
sprintf("atleast once %f percent N = %d", 100 - tab_per[["0"]]-tab_per[18], nrow(df2_)-tab_count[["0"]]-tab_count[18] )
```


```{r}
# Airplane Mode
tab_count <- table(df2_$Q3.2_4,useNA = c("always"))
tab_per <-  100*prop.table(table((df2_$Q3.2_4),useNA = c("always")))
print(tab_count)
print(tab_per)
print(tab_per[["0"]])
print(tab_per[19])
sprintf("atleast once %f percent N = %d", 100 - tab_per[["0"]]-tab_per[19], nrow(df2_)-tab_count[["0"]]-tab_count[19] )
```

```{r}
# Notification Managemnet Apps
tab_count <- table(df2_$Q3.2_5,useNA = c("always"))
tab_per <-  100*prop.table(table((df2_$Q3.2_5),useNA = c("always")))
print(tab_count)
print(tab_per)
print(tab_per[["0"]])
print(tab_per[24])
sprintf("atleast once %f percent N = %d", 100 - tab_per[["0"]]-tab_per[24], nrow(df2_)-tab_count[["0"]]-tab_count[24])
```


### Compare with Negative Experiences
```{r}
df2_ <- copy
df2_ <- df2_[  , c("Q3.2_1","Q3.2_2" , "Q3.2_3" , "Q3.2_4" ,"Q3.2_5" ,"Q164")]

df2_$Q164<- factor(df2_$Q164, levels = c("0", "1-2", "3-5", "6-10", "11-20", "More than 20", ordered= TRUE))

#remove NAs
df2_$Q164 <- as.character(df2_$Q164)
df2_ <- df2_[(df2_$Q164 )!= "NA", ]
df2_ <- df2_[! is.na(df2_$Q164 ), ]
df2_ <- df2_[! is.na(df2_$Q3.2_1 ), ]
df2_ <- df2_[! is.na(df2_$Q3.2_2 ), ]
df2_ <- df2_[! is.na(df2_$Q3.2_3 ), ]
df2_ <- df2_[! is.na(df2_$Q3.2_4 ), ]
df2_ <- df2_[! is.na(df2_$Q3.2_5 ), ]
```


```{r}
# df2_<- copy[  , c( "Q3.2_1","Q3.2_2" , "Q3.2_3" , "Q3.2_4" ,"Q3.2_5", "Q164")]
df2_ <- df2_ %>% mutate_if(is.factor, as.numeric)
```

#### Mean use grouped by Instances of Negative Experiences
```{r}
# DND
df2_ %>%  group_by(df2_$Q164) %>% summarise(mean_DND = round(mean(Q3.2_1, na.rm = TRUE), 2), median_DND = median(Q3.2_1, na.rm = TRUE), sd_DND = sd(Q3.2_1, na.rm = TRUE))
```

```{r}
#silent mode
df2_ %>%  group_by(df2_$Q164) %>% summarise(mean = round( mean(Q3.2_2, na.rm = TRUE),2), median = median(Q3.2_2, na.rm = TRUE), sd = sd(Q3.2_2, na.rm = TRUE))
```

```{r}
#turn off device
df2_ %>%  group_by(df2_$Q164) %>% summarise(mean = round(mean(Q3.2_3, na.rm = TRUE),2), median = median(Q3.2_3, na.rm = TRUE), sd = sd(Q3.2_3, na.rm = TRUE))
```

```{r}
#airplane mode
df2_ %>%  group_by(df2_$Q164) %>% summarise(mean = round( mean(Q3.2_4, na.rm = TRUE),2), median = median(Q3.2_4, na.rm = TRUE), sd = sd(Q3.2_4, na.rm = TRUE))
```

```{r}
#notification mgmt apps
df2_ %>%  group_by(df2_$Q164) %>% summarise(mean = round(mean(Q3.2_5, na.rm = TRUE),2), median = median(Q3.2_5, na.rm = TRUE), sd = sd(Q3.2_5, na.rm = TRUE))
```



#### Correlation tests
```{r}
t <- cor.test(df2_$Q164, df2_$Q3.2_1, method = "spearman",exact=FALSE)
t
pvals <- c(t$p.value)

t <- cor.test(df2_$Q164, df2_$Q3.2_2, method = "spearman",exact=FALSE)
t
pvals <- append(pvals, t$p.value)

t <- cor.test(df2_$Q164, df2_$Q3.2_3, method = "spearman",exact=FALSE)
t
pvals <- append(pvals, t$p.value)

t <- cor.test(df2_$Q164, df2_$Q3.2_4, method = "spearman",exact=FALSE)
t
pvals <- append(pvals, t$p.value)

t <- cor.test(df2_$Q164, df2_$Q3.2_5, method = "spearman",exact=FALSE)
t
pvals <- append(pvals, t$p.value)

print(pvals)
adj_pvals <- pvals*5
print(adj_pvals)


#earlier code. does not specify correlation method
# source("http://www.sthda.com/upload/rquery_cormat.r")
# c <- rquery.cormat(df2_)
# print(c$r)
# print(c$p)
# padj <- apply(c$p, 2, p.adjust, method = "bonferroni")
# print(padj)
```

```{r}
#normality tests
shapiro.test(df2_$Q3.2_1)
shapiro.test(df2_$Q3.2_2)
shapiro.test(df2_$Q3.2_3)
shapiro.test(df2_$Q3.2_4)
shapiro.test(df2_$Q3.2_5)
shapiro.test(df2_$Q164)
#p-values << 0.05 => all of them are non-normal distributions
```



#### Kruskal wallis test
```{r}
result = kruskal.test(Q164 ~  Q3.2_1  ,   data = df2_) 
print(result)
pvals <- c(result$p.value)

result = kruskal.test(Q164 ~  Q3.2_2  ,   data = df2_) 
print(result)
pvals <- append(pvals, result$p.value)

result = kruskal.test(Q164 ~  Q3.2_3  ,   data = df2_) 
print(result)
pvals <- append(pvals, result$p.value)

result = kruskal.test(Q164 ~  Q3.2_4  ,   data = df2_) 
print(result)
pvals <- append(pvals, result$p.value)

result = kruskal.test(Q164 ~  Q3.2_5  ,   data = df2_) 
print(result)
pvals <- append(pvals, result$p.value)


print(pvals)
adj_pvals <- pvals*5
print(adj_pvals)

```


###Extras
#### Text responses
```{r}
df <- copy[, c("Q3.3")]
df <- df[! is.na(df$Q3.3 ), ]

write.table(df, file = "Features-Q3.3.txt", sep = "\t",row.names = FALSE)

df <- copy[, c( "Q3.2_1","Q3.2_2" , "Q3.2_3" , "Q3.2_4" ,"Q3.2_5", "Q3.3")]
```
```{r}
sprintf("%s", df2_[130,"Q3.3"])
```

```{r}
df <- copy[  , c("Q153","Q144" ,"Q3.1", "Q3.2_1","Q3.2_2" , "Q3.2_3" , "Q3.2_4" ,"Q3.2_5" ,"Q3.3")]
df$Negative_experiences <- copy$Q164 
```

#### No. of notifications in the last one hour
```{r}
100*prop.table(table( df$Q153 ))
table( df$Q153)
nrow(df)
#head(df)
```

#### Frequncy of picking up the phone for addressing notifications
```{r}
table( df$Q144)
100 * prop.table(table( df$Q144 ))
```

```{r}
summary(df$Q144)
```


#### Screen Waking up patterns
```{r}
summary(df$Q3.1)
100*prop.table(table((df$Q3.1)))
```






#### Anova test
```{r}
# one.way <- aov(Q164 ~ Q3.2_1 + Q3.2_2 + Q3.2_3+ Q3.2_4 + Q3.2_5 , data = df2_)
# summary(one.way)
# 
# a1 <- aov(Q164 ~ Q3.2_1, data = df2_)
# summary(a1)
# 
# b1 <- aov(Q164 ~ Q3.2_2, data = df2_)
# summary(b1)
# 
# c1 <- aov(Q164 ~ Q3.2_3 , data= df2_)
# summary(c1)
# 
# c1 <- aov(Q164 ~ Q3.2_4 , data= df2_)
# summary(c1)
# 
# c1 <- aov(Q164 ~ Q3.2_5 , data= df2_)
# summary(c1)
```

